---
title: "空间广义线性混合效应模型及其应用"
subtitle: "2018届硕士学位论文答辩"
author: "学生：黄湘云\\and 导师：李再兴"
institute: "中国矿业大学（北京）\\and 理学院"
date: "\\today"
documentclass: beamer
output: 
  beamer_presentation: 
    citation_package: natbib
    theme: Singapore
    fonttheme: structurebold
    fig_caption: yes
    incremental: no
    keep_tex: yes
    latex_engine: lualatex
    slide_level: 2
    template: ../latex/default.latex
    toc: yes
section-titles: false
header-includes:
    - \usepackage{ctex}
    - \usecolortheme[named=SpringGreen4]{structure}
    - \usepackage[default]{sourcesanspro}
biblio-title: 参考文献
bibliography: refer.bib
biblio-style: apalike
link-citations: yes
colorlinks: yes
linkcolor: SpringGreen4
classoption: "hyperref,x11names,UTF8"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, collapse = TRUE, fig.align = 'center',
                      fig.showtext = ifelse(.Platform$OS.type != 'unix',FALSE,TRUE),
                      out.width = '.7\\textwidth', highlight = FALSE )
```

# 引言

## R Markdown

This is an R Markdown presentation [@bookdown2016CRC]. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# 算法

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


## 语法高亮



